Rapid and Accurate Global PTM Discovery (G-PTM-D) Using Post-Acquisition Spectral Calibration and Defined Mass Windows

### 2017-07-10 paper.tex
yey

Many peptide residue modification types are known, and databases containing detailed information about such modifications are readily available\cite{Creasy_2004}.
Information about a modification often includes the chemical or isotopic composition, mass, specificity to certain residues, and possible restriction of placement to peptide or protein termini.
Protein databases such as UniProt include information on the localization of specific modifications to specific residues in the protein, but this information is incomplete.
Despite the extensive cataloging of the different possible protein modifications, their comprehensive discovery and identifications in complex biological samples has continued to pose a challenge for proteomics\cite{Olsen_2013}.

>>>>

Many types of post-translational modification (PTM) are known, and databases containing detailed information about such modifications are readily available\cite{Creasy_2004}.
Information about a modification often includes the chemical or isotopic composition, mass, specificity to certain residues, and possible restriction of placement to peptide or protein termini.
Protein databases such as UniProt include information on the localization of specific modifications to specific residues in the protein, but this information is incomplete.
Despite the extensive cataloging of the different possible protein modifications, their comprehensive discovery and identification in complex biological samples has continued to pose a challenge for proteomics\cite{Olsen_2013}.
